---
title: "Homework 10"
author: "Jeff Nieman"
date: "April 3, 2016"
output: html_document
  

---

##Assignment Approach
This homework focuses on pulling data from a New York Times API and converting from the JSON code into an R data base.  First I needed to apply for a key.  I then decided to focus on the geographical site pulling a list of twenty populated German cities.

```{r, warning = FALSE, message = FALSE}
library(RJSONIO)
library(RCurl)
q2 <- getURL("http://api.nytimes.com/svc/semantic/v2/geocodes/query.json?feature_class=P&country_code=DE&feature_class=P&api-key=964b66751b69f8042571892d7a0670bd:10:74813960")
head(q2,3)
```

##Parsing and putting data into R data frame
I used the "fromJSON"" function, then placed the data into a data frame using "sappy".

```{r}
q3 <- fromJSON(q2)
head(q3)
q4 <- q3$`results`
head(q4,3)
q5 <- data.frame(t(sapply(q4,c)))
head(q5,3)
```

#Improving the data frame
I cleaned up the data frame for usability by keeping only the most useful columns and renaming them for readability.

```{r}
q6 <- subset(q5[,c(5:7,9,11,16)])
colnames(q6) <-c("City", "Latitude", "Longitude", "Population", "Country", "State")
q6
```


